Security Audit of Safeplug

### 2014-02-07 report/bibliography.tex
Discussion section and import from old report to new.

@@

@@

>>>>

\bibitem{amorbot} The Tor Project. ``Orbot: Proxy with Tor.'' \emph{Google Android Market}. Accessed 7 February 2014, \url{https://play.google.com/store/apps/details?id=org.torproject.android}

@@

\bibitem{dropbear} Johnston, Matt. ``Dropbear SSH.'' \url{https://matt.ucc.asn.au/dropbear/dropbear.html}

@@

\bibitem{orbot} ``Tor on Android.'' \emph{Tor Project.} Accessed February 2014. \url{https://torproject.org/docs/android.html.en}

### 2014-02-07 report/design.tex
added TODO items in paper
Discussion section and import from old report to new.

>>>>

\subsection{Hardware}
We opened up the Safeplug device to look at the internals.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  We identified an SD card slot, Lan transformer, and Ethernet transceiver on the top of the board.  On the bottom, we found flash memory and the integrated circuit.

\begin{figure}[htb]
\centering
\begin{subfigure}[b]{.3\textwidth}
  \includegraphics[width=\textwidth]{safeplug_top}
  \caption{Top of the board inside the Safeplug device.}
  \label{fig:top}
\end{subfigure}%
\qquad
\begin{subfigure}[b]{.3\textwidth}
\includegraphics[width=\textwidth]{safeplug_bottom}
\caption{Bottom of the board inside the Safeplug device.}
\label{fig:bottom}
\end{subfigure}
\caption{Safeplug circuit board after the teardown.}
\end{figure}

\subsection{Software}
\label{software}
We determined the software on the device from analyzing network traffic logs of the activation process (as described below) and accessing the device via SSH (as described in Section~\ref{sec:SSH}).

\subsubsection{Initial Plugin Behavior}
Before allowing the Safeplug box to be connected to the outside world, we attached it to a home connection setup formed by a computer with two network cards and then captured traffic both inside that network and between the network and the internet.  The internal network card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.  The other card was the connection to the internet.  We used Wireshark to analyze the network data that we captured \cite{wireshark}.

Analysis of the TCP dump showed that the Safeplug box repeatedly queried the local DNS server for two items: \url{pogoplug.com} and the NIST standardized time.  The first query for the time was to \url{www.nist.gov}, and subsequent queries included \url{nist1-chi.ustiming.org}, \url{nist1-ny.ustiming.org}, \url{time-nw.nist.gov}, and \url{nist1.symmetricom.com}.  Queries about pogoplug were mostly for \url{service.pogoplug.com} but after that set was tried \url{secure.pogoplug.com} was attempted once.  While it was only connected to the local network, we also did a scan of all the ports of the Safeplug and only port 80 was open.

\subsubsection{Activation and Update Traffic}
\label{updatetraf}
After establishing the initial update behavior, we connected the other end of our homemade router back to the internet and captured traffic on both the network interfaces. As we had seen previously, the first effort of the Safeplug was to query for \url{service.pogoplug.com} and connect, and the send a POST/XML request to that server containing a 16 byte numerical string of type \verb!nid!, \verb!0x0! as \verb!flags!, and a field called \verb!pingdata! with length of 423 bytes and undiscernable contents.  In future work, we hope to explore the contents of this automatic connection with the Pogoplug servers to discover what information is being passed along.

The client computer then navigated to the Pogoplug website to complete the activation processes.  Each step of the process resulted in both TCP and UDP traffic between the Safeplug box and the pogoplug servers.  Most interesting was the update step in which the Safeplug box knew to request a script from \url{<update server IP>/svc/upgrade/safeplug\_switch.sh}.  Since this operation occured over normal HTTP, we were able to use \verb!curl! to recover the same script and examine it to discover the contents of the upgrade.

The upgrade script shows (and the network traffic confirms) that the box downloads and installs the following \verb!.tgz! files: 
\begin{fileName}
safeplug_lighttpd, safeplug_lighttpd_config, safeplug_wget, safeplug_certs, safeplug_gohelper, safeplug_tor, safeplug_tor_config, safeplug_privoxy, safeplug_privoxy_config
\end{fileName}
  Each file is compared to an MD5 hash before being unzipped and installed.  Details about the software found on the Safeplug are discussed in Section \ref{software}.  After the two lighttpd installations, a process called \verb!hbplug! is killed and lighttpd is started.  After the certs are downloaded, the current \verb!/usr/local/ssl! is overwritten with the new certs.  The \verb!go\_helper! is added to the \verb!/opt/xce/sbin! folder, and contains binary files with names related to update and upgrade (which we hope to decompile in future work).

After completing the installations, a default Safeplug configuation file is written with use of Tor set to 1.  (More information about the configuration in Section \ref{spconfig}.)  Finally, the old \verb!rcS! file in \verb!/etc/init.d! is replaced with commands to start lighttpd, tor and privoxy, and the LED on the front of the device is set to green after the completion of the upgrade. This means that the green LED indicates an up-to-date, internet-connected Safeplug, rather than anything about the use of TOR.

\subsubsection{Traffic After Activation}
After the activation and the configuration of the Safeplug as a proxy, all traffic was through the Tor network.  The Safeplug connected to a directory to learn about different relays and seemed to cycle through a small set around the world for different connections.  This demonstrates that Tor is working as expected.  If there is any ``phone-home'' being done by the device after Tor has been turned on, then it is doing so through the Tor network.

\subsubsection{Software on the Safeplug}
As would be suspected from the analysis of the update script described above in Section \ref{updatetraf}, the installed software is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  Privoxy is a ``non-caching web proxy with advanced filtering capabilities for enhancing privacy, modifying webpage data and HTTP headers, controlling access, and removnig ads and other obnoxious Internet junk'' and it specifically advertises its ``flexible configuration'' \cite{privoxy}.  Privoxy is also open source.  All three pieces of software appear to be there with default configuration files (with all appropriate citations and comments present).  The fourth piece of software discovered on the device, which does not seem to be installed during the activation process is the Dropbear SSH server and client, used to support SSH access to the device \cite{dropbear}.  The Safeplug uses its own configuration files to determine how these pieces of software are set up and used.

\subsubsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the important details from the configuration page (whether to use Tor, whether to be a relay, whether to adblock) as well as a hidden option about whether to be an exitrelay for the Tor network.  This is not documented anywhere on the site, so enabling this option would likely require SSH access to discover it, thereby breaking the warranty, but it is interesting that this option is available.  The version file is likely used for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.

These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable lighttpd, privoxy, and tor.  As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf! file to set which Tor configuration file (regular, relay or exitrelay) to use.

### 2014-02-07 report/discussion.tex
Discussion section and import from old report to new.

-does this device have a real market/purpose?

-did not test on mobile devices

>>>>

\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the cross-site attack.  A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts, that must be returned by the browser when making the POST request to the RPC server (CITE).  Although someone doing a cross-site scripting attack such as the one described above could get the cookie sent, if the cookie is set correctly, then the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

\subsection{Structural Problems}
However, there are much more significant structural problems with implementing a Tor connection via an HTTP proxy.  Several of the usability problems involve user awareness and vigilance.  For example, cookies and fingerprinting problems mean that users could still be tracked across websites, regardless of whether the ad-block functionality on the Safeplug is enabled.  This poses an unreasonable stress on users who must be aware of the their browsing practices and does not bode well for the advertised security and anonymity.

One type of client that deserves special attention is a non-Android mobile phone user.  Although the Tor Project publishes an Android app called Orbot on the Android Market \cite{orbot} which is supported for Android versions 2.3 and later \cite{amorbot}, there are no official Tor apps for iPhones or other non-Android devices.  Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.  If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.  Additionally, the user may have to disable the proxy whenever they move to a different network, and remember to re-enable it when they want to use Tor.  This is certainly not transparent usability.  Users who are truly concerned about anonymity online should eschew the Safeplug and purchase a device that supports the Tor Browser Bundle or other Tor Project software.

\subsection{Opportunities}
Despite all the structural problems, is there a room or a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a computer that can run the Tor browser bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging classes of ``smart home'' devices which may connect to the internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains lots of identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silent disabling of Tor in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

### 2014-02-07 report/implementattacks.tex
Discussion section and import from old report to new.

\subsection{Gaining Access through SSH}

\subsection{Insider Attack}

@@

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
\end{enumerate}

@@

>>>>

As we discovered during the software analysis, the Safeplug has a remote procedure call (RPC) capability.  This is a script called \verb!xspctrl! found in \verb!/opt/xce/html/svc! and it contains various options.  Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.  None of them require any arguments in the POST string.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{disabletor}
\caption{Disabling Tor as an insider attack.}
\label{disable}
\end{center}
\end{figure}

\subsection{Insider Attack}
Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.  All the attacker would need to know is the IP of the device.  It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.  Figure \ref{disable} shows an example of this attack.

This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless the happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

This seems like a fairly important vulnerability and requires action from Pogoplug to fix.  Since the purpose of these RPC operations is unclear without access to more of the source code, it is possible that they could be disabled entirely.  If not, perhaps there is some authentication protocol that could be implemented.  The challenge of such a protocol from a user's point of view is that valid access would be infrequent so giving a user a password to remember would be a poor experience.

@@

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: \url{http://<IP address>/svc/xspctrl/disableTor} (See Appendix \ref{App:AppendixA}).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
\end{enumerate}

@@

\subsection{Gaining Access through SSH}
\label{sec:SSH}
    \subsubsection{Accessing the Device}
    Safeplug runs an RPC server that allows the enabling of SSH access via HTTP. SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same (although the Pogoplug support staff note that SSH access breaks the warranty!) \cite{ceadmin}:
\begin{fileName}
curl --data ``'' http://<IP-of-Safeplug>/svc/xspctrl/enableSSHD
ssh root@<IP-of-Safeplug>
password: ceadmin
\end{fileName}

Obviously having a publically available root password means that SSH can be done effectively without authentication.  We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.  Before the activation and update procedure, SSH was not available.  The simple \verb!Hbplug! software on the box could not accept this RPC call.  However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

### 2014-02-07 report/resultsSoftware.tex
Discussion section and import from old report to new.

\subsubsection{Website Attack}
We think it is also possible that an external website could perform this attack by returning the correctly formatted POST string.  Setting this up is future work.

>>>>

\subsubsection{Website Attack}
An external website can also perform this attack by returning a correctly formatted POST string.  This executes the same functionality as the Insider Attack, but the attacker does not need to be on the local network or know the IP address of the Safeplug.  Instead, the attacker (who could be any malicious actor with access to a web server) can just send a POST request to every IP in the common ranges of local addresses in home networks, 192.168.0.0/24 and 192.168.1.0/24.  We implemented this attack with less than 30 lines of Javascript code (See Appendix A).  The following steps are necessary for the attack to be successful:

\begin{enumerate}
\item Set up a web page with the crafted Javascript code, which will send a POST request of the following format to all addresses in the range: http://$<$IP address$>$/svc/xspctrl/disableTor (See Appendix A).
\item Send the malicious link to a user in the targeted private network.
\item Once the user clicks the link and loads the malicious site, the correctly formatted POST request will be sent to every IP address in the ranges.  
\item Tor is disabled silently.  The user must check or refresh her settings page to learn that Tor is turned off.  
\end{enumerate}

This exploits the RPC server in the same manner that the Insider Attack does.  While this attack requires a greater amount of time because the local IP address of the Safeplug must be guessed via search, but the number of private address spaces is small, and the space likely to be occupied by a Safeplug on a home network is even smaller.

The largest observed time to send requests to the 192.168.0.0/24 space was ~400 milliseconds; the entire attack costs ~800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

In addition to disabling Tor, the attacker can modify any other settings on the device.  This includes: enabling/disabling Tor, enabling/disabling ad-blocking, enabling/disabling the use of the device as a Tor relay node [note: this requires the user to do additional setup], enabling/disabling the use of the device as an exit node (if it is already a relay).  Lastly, the attacker can also modify the user's whitelist of sites that should not be routed through Tor.  This whitelist attack is particularly dangerous because the change is silent and much harder for the user to notice the addition of a single website to the whitelist than a global loss of Tor.  (Removal of a webpage from the whitelist is likely to to cause usability problems and be more evident.)

### 2014-02-07 report/usability.tex
Discussion section and import from old report to new.

After we finished our configuration, we were taken to our settings.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn on/off Tor, add whitelisted websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they couldn't read their web pages (if they weren't in their native language), or if they couldn't log into their accounts (some web sites will lock a user out if they try to login from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.  We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account.

@@

This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.  Although normal use does follow this model of persisting logins across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.

>>>>

After we finished our configuration, we were taken to our settings.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn on/off Tor, add white-listed websites, turn on/off ad-blocking, and turn on/off the ability of our device to be a relay node.

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.  We were also prompted with the page in Figure~\ref{fig:funnygoogle} when we tried to log into our Google account.

@@

This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.  Although normal use does follow this model of persisting logged in status across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.
